Probability of causal contact between interstellar civilizations through MonteCarlo simulations

### 2019-12-29 Sec_methods.tex
preparando todo para scholar one
seccion leyes de prob

\begin{figure}
   \centering
   \includegraphics[width=0.5\textwidth]{scheme.pdf}
   \usecaption{F_scheme} \label{F_scheme}
\end{figure}

\begin{figure*}
   \centering
   \includegraphics[width=0.8\textwidth]{Messages_01.pdf}
   \usecaption{F_messages} \label{F_messages}
\end{figure*}

@@

The initially growing communicating sphere, is shown over
space--time diagrams, where time is represented on the horizontal
direction, and space is represented in the vertical direction.
%
In the upper panel (a), the sphere is growing as the surface of first
contact has not reached the maximum distance.
%
In the middle panel (b) it has reached the maximum distance, so that
it remains at the same size.
%
After a Doomsday event (bottom panel, b), the signals can still be
observed, but the surface of last contact grows.
%
We also show in this Figure a schematic representation of two
emitters, E$_1$ and E$_2$, that reach each other at different times.
%
The time span for E$_i$ is (A$_i$ , D$_i$) , for $i = {1, 2}$.
%
Emitter $i$ can listen to emitter $j$ between C$_{ij}$ and B$_{ij}$.
%
The type and length of causal contact in both directions depend on the
distance and time lag between the awakening events, the maximum
distance that a signal can reach and the time period in which each
emitter is active.
%
In the Fig.~\ref{F_messages} we show a schematic representation of the
possible cases in which a \ceti A can be in causal contact with a
\ceti
B which appears later.
%
The duration of the causal contact in one direction depends on several
factors, mainly $\Delta$t~A , $\Delta$t~C , and $\Delta$X.

@@

The exponential distribution of lifespan and waiting times is
justified by considering that the process of appeareance of life in
the galaxy is homogeneous and stationary.
%
Equivalently there is no preferred location within the GHZ for the
spontaneous appeareance of life, and that the emergence of a
civilization is independent of the existence of previous civilizations
in the galaxy.
%            
This is equivalent to proposing a Poisson process for the emergence of
\cetis, since there is a close relation between the number of events in
time or space and the waiting time or separation, respectively.
%
That is, these are two alternative approaches to describing the same
process, a Poisson distribution for the number of events implies an
exponential distribution for their separations, and viceversa.
%
It should be emphasized that the exponential laws used in this work
are assumed, although instead of analyzing results from a particular
parameter chosen ad--hoc, we explore the hypothesis space and analyze
the impact of the values of these parameters on the results.

@@

@@

\begin{figure} \centering
   \includegraphics[width=0.5\textwidth]{F1.pdf}
   \usecaption{F_number_of_contacts} \label{F_number_of_contacts}
\end{figure}

>>>>

\begin{figure}
   \centering
   \includegraphics[width=0.5\textwidth]{F_scheme.pdf}
   \usecaption{F_scheme} \label{F_scheme}
\end{figure}

\begin{figure*}
   \centering
   \includegraphics[width=0.8\textwidth]{F_messages.pdf}
   \usecaption{F_messages} \label{F_messages}
\end{figure*}

@@

The initially growing communicating sphere, is shown over
space--time diagrams, where time is represented on the horizontal
direction, and space is represented in the vertical direction.
%
In the upper panel (a), the sphere is growing as the surface of first
contact has not reached the maximum distance.
%
In the middle panel (b) it has reached the maximum distance, so that
it remains at the same size.
%
After a Doomsday event (bottom panel, b), the signals can still be
observed, but the surface of last contact grows.
%
We also show in this Figure a schematic representation of two
emitters, E$_1$ and E$_2$, that reach each other at different times.
%
The time span for E$_i$ is (A$_i$ , D$_i$) , for $i = {1, 2}$.
%
Emitter $i$ can listen to emitter $j$ between C$_{ij}$ and B$_{ij}$.
%
The type and length of causal contact in both directions depend on the
distance and time lag between the awakening events, the maximum
distance that a signal can reach and the time period in which each
emitter is active.
%
In the Fig.~\ref{F_messages} we show a schematic representation of the
possible cases in which a \ceti E can be in causal contact with a
\ceti
R.
%
The duration of the causal contact in one direction depends on several
factors, mainly the lifetimes, the time period between the A events 
and the distance between the two \cetis involved in the causal
contact.

@@

@@

In this work, the exponential distribution of lifespan and waiting
times is justified by considering the hypothesis that the process of
appeareance of life in the galaxy is homogeneous and stationary.
%
That is, there is no preferred location within the GHZ for the
spontaneous appeareance of life, and the emergence of a \ceti is
independent of the existence of previous \cetis in the galaxy.
%            
This is equivalent to proposing a Poisson process for the emergence of
\cetis, since there is a close relation between the number of events
in time or space and the waiting time or separation, respectively
\citep[e.g., ][]{ross_simulation_2012}.
%
That is, these are two alternative approaches to describing the same
process, a Poisson distribution for the number of events implies an
exponential distribution for their separations, and viceversa.
%
It should be emphasized that the exponential laws used in this work
are assumed as part of the working hypothesis, and instead of
analyzing results from a particular parameter chosen ad--hoc, we
explore the hypothesis space and analyze the impact of the values of
these parameters on the results.

@@

\begin{figure} \centering
   \includegraphics[width=0.5\textwidth]{F_number_of_contacts.pdf}
   \usecaption{F_number_of_contacts} \label{F_number_of_contacts}
\end{figure}
